---
title: "Saint Louis Housing Data"
author: "Shraddha Belbase"
date:"December 13, 2018s"
output: html_notebook
---

#Loading Libraries
```{r message=TRUE, warning=FALSE, paged.print=FALSE}
#hsdbhfb
library(dplyr)
library(tidyr)
library(purrr)
library(broom)
# Vector Manipulation
library(stringr)
library(lubridate)
library(forcats)
# Presentation
library(ggplot2)
library(GGally)
library(ggthemes)
library(scales)
library(texreg)

```

#Importing the DataSet
```{r}
data_cocs <- read_csv("data/stl_county_sales.csv")
```

#Missing Obervations
Before starting analyzing our data, let's if there are any Missing Observations in our dataset.
```{r}
pdat <- data_cocs %>%
  summarize_all (
    funs(sum(is.na(.)))
) %>%
  gather(
    vars, isna_cnts
  )
 knitr::kable(pdat)
```

```{r}
data_new <- data_cocs %>%
  mutate(id_zip = as.character(id_zip),
         date_trans = mdy(date_trans),
         #date_year = year(date_trans),
         id_division = if_else(id_market == "East70", "East70", "County Remainder"),
         resid = log(appr)-log(price_trans))
 
```
Looks like we do not have any Missing Observations in our dataset.
```{r}
model <- lm(resid ~ as.character(year(date_trans)) + age + I(age^2) + I(age^3) + log(area)+ log(sfla) + id_division, data = data_new)
summary(model)
```

#Missing Observations?
Are there any missing observations in the dataset?
```{r}
 ggplot(data = data_new)+
   geom_bar(mapping = aes(x = id_market))+
   labs(
    title = "Housing Sale Distribution in different Areas",
    x = "ID", y ="Count"
  
    )
```
This shows that the most amount of houses were sold in the South of Saint Louis and the least in East70.
#Transations by age
Lets plot a density plot to see the corelation between age of the house and the transaction
```{r}
 ggplot(data = data_new, aes(x = age)) +
  geom_density()
```

This shows that the houses between the age 30 to 60 have a higher transaction density compared to other ages.

#East 70
Lets now observe the data in East70 and analyze the housing patterns in this area.
First off, lets start by filtering data. The code below filters the data and gets the only ones from East70
```{r}
data_update <- data_new %>%
  filter (id_division == "East70")%>%
mutate(
    date_year = year(date_trans))

```
Let's now look at the box plot
```{r}
data_update <- data_new %>%
  filter (id_division == "East70")%>%
mutate(
    date_year = year(date_trans))

pdat <- data_update %>%
  group_by(date_year)
 

ggplot(pdat, aes(as.character(date_year),log(price_trans))) +
  geom_boxplot()+
  #geom_line()+
 
  labs(
    title = "",
    x = "", y =""
  )

```
```{r}
pdat <- data_update %>%
  nest(
    -date_year
  ) %>%
  mutate(
    Quantiles = map(data, ~quantile(.$area))
  ) %>%
  unnest(
    map(Quantiles, tibble::enframe)
  ) %>%
  mutate(
    name = factor(name, levels = c("0%", "25%", "50%", "75%", "100%"))
  ) %>%
  arrange(
    date_year
    )%>%
  spread(
    name, value
    )

knitr::kable(pdat, digits = 3)
```

```{r}
pdat <- data_update %>%
  nest(
    -date_year
  ) %>%
  mutate(
    Quantiles = map(data, ~quantile(.$sfla))
  ) %>%
  unnest(
    map(Quantiles, tibble::enframe)
  ) %>%
  mutate(
    name = factor(name, levels = c("0%", "25%", "50%", "75%", "100%"))
  ) %>%
  arrange(
    date_year
    )%>%
  spread(
    name, value
    )

knitr::kable(pdat, digits = 0)
  
```

```{r}
pdat <- data_update %>%
  nest(
    -date_year
  ) %>%
  mutate(
    Quantiles = map(data, ~quantile(.$sfla))
  ) %>%
  unnest(
    map(Quantiles, tibble::enframe)
  ) %>%
  mutate(
    name = factor(name, levels = c("0%", "25%", "50%", "75%", "100%"))
  ) %>%
  arrange(
    date_year
    )%>%
  spread(
    name, value
    )

knitr::kable(pdat, digits = 0)
  
  
```



```{r}
pdat <- data_new %>%
  group_by(id_division, date_trans)%>%
  count(date_trans)

 ggplot(pdat, aes(date_trans,n,colour = id_division))+
  geom_smooth()+
  theme_hc() + scale_colour_hc()
  
 
```

```{r}
pdat <- data_new %>%
  mutate(
    date_year = year(date_trans)
  )
 

ggplot(pdat, aes(as.character(date_year),log(price_trans))) +
  geom_boxplot() +
  labs(x = NULL, y =NULL)
```
Mean is increasing till 2008 and slightly decreasing in 2009 and going back again.
